A Survey on Ordered Binary Decision Diagrams

### 2015-09-14 paper.tex
Add section Symbolic model checking using OBDDs
Fix heading
Add Symbolic model checking intro

>>>>

\section{Symbolic Model Checking}
\label{sec:symbolic-model-checking}

One specific application of reduced ordered binary decision diagrams is 
\textit{symbolic model checking}, introduced by Burch et al.~\cite{BURCH90} in
1990. \textit{Symbolic}, because the state space is not represented explicitly
but symbolically by utilizing OBDDs to represent $\mu$-Calculus formulas.
In~\cite{BURCH90}, Burch, Clarke, McMillan, Dill and Hwang derived an efficient
decision procedures for CTL model checking as well as satisfiability of LTL
formulas, strong and weak observational equivalence of finite transition systems
and language containment for finite $\omega$-automata by introducing a new
$\mu$-Calculus model checking algorithm. However, this survey just outlines the
$\mu$-Calculus and the efficient decision procedures for CTL model checking.

The main idea behind this approach is to represent the state space symbolically,
instead of explicitly with e.g. a state table. Such explicit state tables may grow
exponentially with the number of concurrent components, because the state space
does so. Commonly, this is referred to as the
\textit{state explosion problem}~\cite{BURCH90, MCMILLAN92}. \tbr
